Sparse Function-space Representation \\ of Neural Networks

### 2023-05-14 paper/main.tex
started experiments section
added intro for sequential leqrnaing

@@

>>>>

We have presented a method for converting any trained neural network into a sparse function-space representation.
In this section, we demonstrate how sequential learning methods can benefit from our function-space representation.

@@

Our experiments seek to answer the following questions:
\begin{itemize}
  \item Does NN2SFR caputure good uncertainty estimates
\end{itemize}
